Attention Towards Distance Education Tools During COVID-19 Pandemic: Evidence from Google Trends

### 2021-12-16 Paper_online_Learning.tex
update introduction

The first confirmed case of Covid-19 was reported from Sri Lanka on 27 January 2020 with a person who came to Sri Lanka as a tourist. The first locally transmitted COVID-19 case in Sri Lanka was then reported on 11 March 2020 followed by an increasing trend of the COVID-19 confirmed cases. In response to this increasing trend of COVID 19 cases, lockdowns and curfews were imposed several times across the country with the aim of reducing the spread of the virus. As of 29 September 2021, 515524 cases of COVID-19 have been reported in Sri Lanka, resulting with 12786 deaths \autocite{HealthSL2020,dong2020interactive}.

@@

The ongoing COVID-19 pandemic has brought the world to a standstill. Many sectors have been affected ever since the outbreak of COVID 19, worldwide. Among these many sectors education is one of the most affected sectors with a near-total closures of schools, colleges and universities, all around the world \autocite{daniel2020education}. Figures \ref{fig:covidImpactWorld} shows the evolution of global school closures and reopening since mid February 2020. With the start of the pandemic a near total closure of schools were observed all around the world. In line with that, the Sri Lankan government also ordered to close schools from 12 March 2020 and its planned reopening of schools was delayed several times due to unexpected Covid-19-related circumstances \autocite{wikieducation}. Over time, Africa and Oceania demonstrated better recovery in comparison to other regions with their increasing number of fully open schools (Figures \ref{fig:covidImpactContinent}).

@@

Google Trends is an open source web analytics tool that allows users to interact with Internet search data, which can provide deep insights into population behavior \autocite{nuti2014use}. In this study we test whether the Google Analytics search index series can be used as a proxy of the popularity and the public interest in different distance education solutions. In line with that, this paper makes three fundamental contributions to distance education by exploring three main questions: (1) What is the impact of COVID 19 pandemic on education? (2) What solutions are in place to meet the need of distance education in terms during COVID 19 pandemic? (3) Which distance learning solutions have a wide attention and public interest both at the national and global level?
We primarily analyze quantitative digital footprint data on the internet from December 2019 to August 2021. The resulted google trend footprint provides a fast first step to identify the most popular distance education tools available for different education purposes. It also allows the teachers to narrow down the search space and deepen their exploration on prominent distance education solutions to support their online teaching.

@@

\hypertarget{benefits-of-competition}{%
\subsubsection{Benefits of Competition}\label{benefits-of-competition}}

As Uber was queried more on Google, he was able to find a decrease in complaints of broken credit card machines as the taxis improved their service in response to the increased. Complaints may provide a proxy of the quality of traditional taxis in the city and thus provide a means to investigate the service quality differences in yellow taxis since the arrival of Uber \autocite{willis2020using}.

In total, our approach to employ novel data from a news media outlet to approximate the public interest and Uber's popularity enabled us to illustrate how Uber disrupted the New York City well established taxi market.

Both of these behavioural mechanisms can potentially explain the increase in the number of complaints about taxi service.
\#\# Analysis

\url{https://www.weforum.org/agenda/2020/12/google-most-popular-search-2020/}

Google has analyzed the billions of search requests it processes every day, and identified the terms that have had the highest spike this year compared to 2019. Unsurprisingly, ``coronavirus'' topped the overall list.

The search trends show the impact of the COVID pandemic on so many aspects of life. Relatively obscure teleconferencing company Zoom became a household name (and highly profitable business) as employees adapted to working from home, and friends and families turned to video calls instead of meeting in person .

Google Classroom was one of several online resources that provided education to millions of children affected by school closures. Searches for ``how to foster a dog'' reached an all-time high as social distancing triggered a yearning for the companionship of a pet.

\url{https://www.weforum.org/agenda/2020/12/google-most-popular-search-2020/}

Notably, GT, together with social media, could be use- fully exploited by global and local health agencies, as well as by public health practitioners, as a tool to identify disease-related information needs, social and behavioural barriers to infection control, and misinformation, as well as to better understand sentiment and risk perception associated with health-threatening events such as an Ebola outbreak {[}5, 37{]}. Indeed, analyses of the temporal trend of GT-based query volumes together with their geographic distribution and main topics of searches can furnish a quantifiable and valuable measure of public attention and information needs about a particular communicable disease \autocite{alicino2015assessing}.

The Internet represents a great opportunity for public health agencies to disseminate healthcare-related infor- mation quickly, effectively and cheaply, provided that re- liable news are shared with as much of the population as possible, both in developed and developing countries, where the diffusion of new technologies among the population is rapidly increasing. Google Trends -- a pub- licly available data source -- could be used as a proxy of the proper diffusion of strategies based on health educa- tion messages, allowing to fill the translation gap be- tween best evidence (what some experts know) and practice (what most people do or believe) {[}38{]}. More- over, it could be exploited to determine the level of up- take of information about a public health event. Even during the 2014 Ebola outbreak, some stakeholders lev- eraged new technologies to plan proper communication strategies and address public concern {[}39, 40 \autocite{alicino2015assessing}.

Hara and Kling (2000) argue that more research about online courses from the students' perspective is needed. In a case study of graduate students enrolled in an online course, they found that many aspects of the course frustrated students, and that the instructor remained unaware of the continuing level of frustration. They suggest that many researchers bring an optimistic, romantic view of technology that may dampen their ability to look at hard questions and apply rigorous research methods. Much of the research, they maintain, has been advocacy and theorizing about future possibilities \autocite{wallace2003online}.

As shown in this literature review, the most common applications of Google search data in social science to date have been in economics, finance, and business, though there have also been studies in other fields, including media and technology (Rech, 2007), the entertainment industry (Goel, Hofman, Lahaie, Pennock, \& Watts, 2010), and politics (Reilly, Richey, \& Taylor, 2012). We did not, however, find any studies using Google Trends data in the higher education sector, which is our area of study \autocite{vaughan2014web}. However their (\textcite{vaughan2014web}) fous is on Our study determines whether Google Trends data can be used to estimate or predict academic fame by testing the correlation between search volume data and university ranking data.

@@

Every single step including planning, developing new tools and techniques, conducting awareness programs and workshops about online education, shifting towards online education happens through online due to unexpected massive shutdown worldwide.

>>>>

@@

The ongoing COVID-19 pandemic has brought the world to a standstill. Many sectors have been affected ever since the outbreak of COVID 19, worldwide. Among these many sectors education is one of the most affected sectors with a near-total closures of schools, colleges and universities, all around the world \autocite{daniel2020education}. Figures \ref{fig:covidImpactWorld} shows the evolution of global school closures and reopening since mid February 2020. With the start of the pandemic a near total closure of schools were observed all around the world. Over time, Africa and Oceania demonstrated better recovery in comparison to other regions with their increasing number of fully open schools (Figures \ref{fig:covidImpactContinent}).

@@

Google Trends is an open source web analytics tool that allows users to interact with Internet search data, which can provide deep insights into population behavior \autocite{nuti2014use}. In this study we test whether the Google Analytics search index series can be used as a proxy of the popularity and the public interest in different distance education solutions. In line with that, this paper makes three fundamental contributions to distance education by exploring three main questions: (1) What is the impact of COVID 19 pandemic on education? (2) What solutions are in place to meet the need of distance education in terms during COVID 19 pandemic? (3) Which distance learning solutions have a wide attention and public interest during the COVID-19 pandemic?
We primarily analyze quantitative digital footprint data on the internet from December 2019 to August 2021. The resulted google trend footprint provides a fast first step to identify the most popular distance education tools available for different education purposes. It also allows the teachers to narrow down the search space and deepen their exploration on prominent distance education solutions to support their online teaching.

@@

@@

\hypertarget{discussion-and-conclusion}{%
\subsection{Discussion and Conclusion}\label{discussion-and-conclusion}}

### 2021-12-16 main.Rmd
update introduction

The first confirmed case of Covid-19 was reported from Sri Lanka on 27 January 2020 with  a person who came to Sri Lanka as a tourist.  The first locally transmitted COVID-19 case in Sri Lanka was then reported on  11 March 2020 followed by an increasing trend of the COVID-19 confirmed cases. In response to this increasing trend of COVID 19 cases, lockdowns and curfews were imposed several times across the country with the aim of reducing the spread of the virus. As of 29 September 2021, 515524 cases of COVID-19 have been reported in Sri Lanka, resulting with 12786 deaths [@HealthSL2020; @dong2020interactive].

@@

The ongoing COVID-19 pandemic has brought the world to a standstill.  Many sectors have been affected ever since the outbreak of COVID 19, worldwide. Among these many sectors education is one of the most affected sectors with a near-total closures of schools, colleges and universities, all around the world [@daniel2020education]. Figures \ref{fig:covidImpactWorld} shows the evolution of global school closures and reopening since mid February 2020. With the start of the pandemic a near total closure of schools were observed all around the world. In line with that, the Sri Lankan  government also ordered to close schools from 12 March 2020 and  its planned reopening of schools was delayed several times due to unexpected Covid-19-related circumstances [@wikieducation]. Over time, Africa and Oceania demonstrated better recovery in comparison to other regions with their increasing number of fully open schools (Figures \ref{fig:covidImpactContinent}).

@@

Google Trends is an open source web analytics tool that allows users to interact with Internet search data, which can provide deep insights into population behavior [@nuti2014use]. In this study we test whether the Google Analytics search index series can be used as a proxy of the popularity and the public interest in different distance education solutions. In line with that, this paper makes three fundamental contributions to distance education by exploring three main questions: (1) What is the impact of  COVID 19 pandemic on education? (2) What solutions are in place to meet the need of distance education in terms during COVID 19 pandemic? (3) Which distance learning solutions have a wide attention and public interest both at the national and global level? 
We primarily analyze quantitative digital footprint data on the internet from December 2019 to August 2021. The resulted google trend footprint provides a fast first step to identify the most popular distance education tools available for different education purposes. It  also allows the teachers to narrow down the search space and  deepen their exploration on  prominent distance education solutions to support their online teaching.

@@

### Benefits of Competition
As Uber was queried more on Google, he was able to find a decrease in complaints of broken credit card machines as the taxis improved their service in response to the increased. Complaints may provide a proxy of the quality of traditional taxis in the city and thus provide a means to investigate the service quality differences in yellow taxis since the arrival of Uber [@willis2020using].

In total, our approach to employ novel data from a news media outlet to approximate the public interest and Uber’s popularity enabled us to illustrate how Uber disrupted the New York City well established taxi market.

Both of these behavioural mechanisms can potentially explain the increase in the number of complaints about taxi service.
## Analysis

https://www.weforum.org/agenda/2020/12/google-most-popular-search-2020/

Google has analyzed the billions of search requests it processes every day, and identified the terms that have had the highest spike this year compared to 2019. Unsurprisingly, “coronavirus” topped the overall list.

The search trends show the impact of the COVID pandemic on so many aspects of life. Relatively obscure teleconferencing company Zoom became a household name (and highly profitable business) as employees adapted to working from home, and friends and families turned to video calls instead of meeting in person .

Google Classroom was one of several online resources that provided education to millions of children affected by school closures. Searches for “how to foster a dog” reached an all-time high as social distancing triggered a yearning for the companionship of a pet.

https://www.weforum.org/agenda/2020/12/google-most-popular-search-2020/

Notably, GT, together with social media, could be use- fully exploited by global and local health agencies, as well as by public health practitioners, as a tool to identify disease-related information needs, social and behavioural barriers to infection control, and misinformation, as well as to better understand sentiment and risk perception associated with health-threatening events such as an Ebola outbreak [5, 37]. Indeed, analyses of the temporal trend of GT-based query volumes together with their geographic distribution and main topics of searches can furnish a quantifiable and valuable measure of public attention and information needs about a particular communicable disease [@alicino2015assessing].

The Internet represents a great opportunity for public health agencies to disseminate healthcare-related infor- mation quickly, effectively and cheaply, provided that re- liable news are shared with as much of the population as possible, both in developed and developing countries, where the diffusion of new technologies among the population is rapidly increasing. Google Trends – a pub- licly available data source – could be used as a proxy of the proper diffusion of strategies based on health educa- tion messages, allowing to fill the translation gap be- tween best evidence (what some experts know) and practice (what most people do or believe) [38]. More- over, it could be exploited to determine the level of up- take of information about a public health event. Even during the 2014 Ebola outbreak, some stakeholders lev- eraged new technologies to plan proper communication strategies and address public concern [39, 40 [@alicino2015assessing].

Hara and Kling (2000) argue that more research about online courses from the students’ perspective is needed. In a case study of graduate students enrolled in an online course, they found that many aspects of the course frustrated students, and that the instructor remained unaware of the continuing level of frustration. They suggest that many researchers bring an optimistic, romantic view of technology that may dampen their ability to look at hard questions and apply rigorous research methods. Much of the research, they maintain, has been advocacy and theorizing about future possibilities [@wallace2003online].

As shown in this literature review, the most common applications of Google search data in social science to date have been in economics, finance, and business, though there have also been studies in other fields, including media and technology (Rech, 2007), the entertainment industry (Goel, Hofman, Lahaie, Pennock, & Watts, 2010), and politics (Reilly, Richey, & Taylor, 2012).  We did not, however, find any studies using Google Trends data in the higher education sector, which is our area of study [@vaughan2014web]. However their (@vaughan2014web) fous is on Our study determines whether Google Trends data can be used to estimate or predict academic fame by testing the correlation between search volume data and university ranking data.

@@

Every single step including planning, developing new tools and techniques, conducting awareness programs and workshops about online education, shifting towards online education happens through online due to  unexpected  massive shutdown worldwide.

>>>>

<!--
The first confirmed case of Covid-19 was reported from Sri Lanka on 27 January 2020 with  a person who came to Sri Lanka as a tourist.  The first locally transmitted COVID-19 case in Sri Lanka was then reported on  11 March 2020 followed by an increasing trend of the COVID-19 confirmed cases. In response to this increasing trend of COVID 19 cases, lockdowns and curfews were imposed several times across the country with the aim of reducing the spread of the virus. As of 29 September 2021, 515524 cases of COVID-19 have been reported in Sri Lanka, resulting with 12786 deaths [@HealthSL2020; @dong2020interactive].
-->

@@

The ongoing COVID-19 pandemic has brought the world to a standstill.  Many sectors have been affected ever since the outbreak of COVID 19, worldwide. Among these many sectors education is one of the most affected sectors with a near-total closures of schools, colleges and universities, all around the world [@daniel2020education]. Figures \ref{fig:covidImpactWorld} shows the evolution of global school closures and reopening since mid February 2020. With the start of the pandemic a near total closure of schools were observed all around the world. Over time, Africa and Oceania demonstrated better recovery in comparison to other regions with their increasing number of fully open schools (Figures \ref{fig:covidImpactContinent}).

<!--In line with that, the Sri Lankan  government also ordered to close schools from 12 March 2020 and  its planned reopening of schools was delayed several times due to unexpected Covid-19-related circumstances [@wikieducation].-->

@@

Google Trends is an open source web analytics tool that allows users to interact with Internet search data, which can provide deep insights into population behavior [@nuti2014use]. In this study we test whether the Google Analytics search index series can be used as a proxy of the popularity and the public interest in different distance education solutions. In line with that, this paper makes three fundamental contributions to distance education by exploring three main questions: (1) What is the impact of  COVID 19 pandemic on education? (2) What solutions are in place to meet the need of distance education in terms during COVID 19 pandemic? (3) Which distance learning solutions have a wide attention and public interest during the COVID-19 pandemic? 
We primarily analyze quantitative digital footprint data on the internet from December 2019 to August 2021. The resulted google trend footprint provides a fast first step to identify the most popular distance education tools available for different education purposes. It  also allows the teachers to narrow down the search space and  deepen their exploration on  prominent distance education solutions to support their online teaching.

@@

@@

## Discussion and Conclusion
